Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-20 prop_letter.tex
prop_letter.tex \begin{abstract} Small modification...

\begin{abstract}
\begin{description}
\item [{Background}] In a world of bounded resource, any quantum measurement
can be only performed in finite precision. {\small \par}
\item [{Method}] We model idea of the finite precision measurement as finite
number of intervals, and replace quantum real-valued probability measures
by interval-valued ones. {\small \par}
\item [{Results}] Quantum interval-valued probability measures provide
a unified framework to interpret Gleason's theorem and the Kochen-Specker
theorem on an equal footing. For the cases between them, we found
some legitimate quantum interval-valued probability measures which
cannot be explained by the Born rule. While restricting on only commuting
projectors, the interval-valued probability measures become classical,
and these non-Born interval-valued probability measures disappear. {\small \par}
\item [{Conclusions}] Our research provides a new insight of finite precision
measurement and non-commutativity when formulating quantum theory,
and the Born rule may not be as nature as we used to believe in the
world of finite resource.{\small \par}
\end{description}
\end{abstract}

>>>>

\begin{abstract}
\begin{description}
\item [{Background}] In a world of bounded resource, any quantum measurement
can be only performed in finite precision. {\small \par}
\item [{Method}] We model idea of the finite precision measurement as finite
number of intervals, and replace quantum real-valued probability measures
by interval-valued ones. {\small \par}
\item [{Results}] Quantum interval-valued probability measures provide
a unified framework to interpret Gleason's theorem and the Kochen-Specker
theorem as the limiting cases. For the cases between them, we found
some legitimate quantum interval-valued probability measures which
cannot be explained by the Born rule. While restricting on only commuting
projectors, the interval-valued probability measures become classical,
and these non-Born interval-valued probability measures disappear. {\small \par}
\item [{Conclusions}] Our research provides a new insight of finite precision
measurement and non-commutativity when formulating quantum theory.
Also, the Born rule may not be as nature as we used to believe in
the world of finite resource.{\small \par}
\end{description}
\end{abstract}
